Optimal Task Phasing for End-To-End Latency in Semi-Harmonic Task Systems

### 2024-09-25 paper.tex
abstract

	\begin{abstract}
		ABSTRACT
		- introductory sentence to the topic (optional)
		- describe the issue or main problem (create a need)
		- one sentence detailing your approach (meet the need)
		- list main research results
		- finish with MAIN MESSAGE of the paper
	\end{abstract}

>>>>

	\begin{abstract}
		% - introductory sentence to the topic (optional)
		In the context of automotive systems, the end-to-end latency of a sequence of tasks (a so-called cause-effect chains) is a common metric to ensure correct timing behavior.
		% - describe the issue or main problem (create a need)
		To control the end-to-end latency, proper task configuration is crucial. 
		While the literature considers the configuration of task periods, optimization of task phases to minimize the end-to-end latency is only sparsely discussed.

		% - one sentence detailing your approach (meet the need)
		In this work, we discuss the configuration of task phases to optimize the end-to-end latency of a cause-effect chain.
		% - list main research results
		To that end, we develop a strategy for semi-harmonic task systems, which are very common in industrial applications.
		% - finish with MAIN MESSAGE of the paper
		We prove that our strategy is optimal in the sense that it minimizes the end-to-end latency.
		Furthermore, our evaluation based on a real-world application shows that optimizing task phases can reduce end-to-end latencies significantly. 
	\end{abstract}
